A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-10-18 documents/plm.tex
notes to self

\todo{Should we put general formula here for a pixel predicted using a linear combination of other pixels?
  And the objective function, generally?}

@@

\todo{In what follows, we need to choose consistent notation or terminology about the contiguous data chunks, and other \Kepler\ entities.}

In addition, each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}$.
The train-and-test framework, which includes data out to time $t_{\max}$ but excludes data within $\Delta t$ of the test data,
  effectively assumes that the signals worth preserving have time-scales less than $\Delta t$ but don't recur on time-scales
  shorter than $t_{\max}$.
Those assumptions are good for our purposes but not necessarily ideal for all users:
Short-period exoplanets and certain kinds of stellar variability
  could be wiped out by a model with these settings of the training-data regime.

@@

The train-and-test idea comes into the objective function $\chi^2_{mn}$:
When we are computing the objective function $\chi^2_{mn}$,
  we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
We train the model---that is, set the parameters $a_{mm'}$ and $b_{mk}$---%
  by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{mn}$.
Importantly, and perhaps surprisingly, this is a \emph{different objective function}
  for every target data point (pixel value to be predicted) $I_{mn}$,
  and we have to do a \emph{independent optimization} of the parameters for every pixel value we want to predict.
Since there are about $10^{11}$ total pixel values in the \Kepler\ \todo{what imaging?} data archive,
  this represents one fuck of a lot of optimizations.

@@

We construct the predicted images and the \name\ images how?

What does the interface look like?  What are the run times and so on?

>>>>

@@

In addition, each training data set within which we set the parameters (by optimization) has a finite total time extent $t_{\max}\approx 90$\,d.
The train-and-test framework, which includes data out to time $t_{\max}$ but excludes data within $\Delta t$ of the test data,
  effectively assumes that the signals worth preserving have time-scales less than $\Delta t$ but don't recur on time-scales
  shorter than $t_{\max}$.
Those assumptions are good for our purposes but not necessarily ideal for all users:
Short-period exoplanets and certain kinds of stellar variability
  could be wiped out by a model with these settings of the training-data regime.

@@

The train-and-test idea comes into the objective function $\chi^2_{mn}$:
When we are computing the objective function $\chi^2_{mn}$,
  we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
We train the model---that is, set the parameters $a_{mm'}$ and $b_{mk}$---%
  by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{mn}$.
Importantly, and perhaps surprisingly, this is a \emph{different objective function}
  for every target data point (pixel value to be predicted) $I_{mn}$,
  and we have to do a \emph{independent optimization} of the parameters for every pixel value we want to predict.
That is, every pixel datum $I_{mn}$ we predict will have
  \emph{different} settings of the parameters $a_{mm'}$ and $b_{mk}$.
Since there are about $10^{11}$ total pixel values in the \Kepler\ \todo{what imaging?} data archive,
  this represents one fuck of a lot of optimizations,
  and a lot of parameters to obtain and record.

@@

\todo{HOGG: We construct the predicted images and the \name\ images how?}

\todo{HOGG: We construct the \name\ photometry from the \name\ images how?}

\todo{DFM: What does the interface look like?  What are the run times and so on?}
